---
title: "Incarceration Analysis"
author: "Fred Li"
date: '2022-11-21'
output: html_document
---

```{r echo=FALSE, eval=TRUE, message=FALSE}
source("../source/a4-helpers.R")
source("../source/analysis.R")
```

## Abstract 
Disparities in the criminal justice system have become increasingly apparent in US incarceration statistics since 1970. The effects of shifting policies regarding crime and incarceration have varied across time, place, and jurisdiction. The number of people locked up in prisons is staggering. In this report, we look at incarceration rates from the past to gain insight into the problems we face now and how to solve them going forward.

# Test (TODO: Remove before submission!!)
```{r echo=FALSE}
q1_string <- test_query1()
num <- 5
```
As you know, this is a markdown report. The [R Markdown Cheatsheet](https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf) is **useful!**

* Here's a test of a dynamic variable. Say **"`r q1_string`!!!** 
* Here's another test. A vector
of numbers: `r test_query2(num)`.

Recall that _{r echo=TRUE}_ can be used to display the code, 
which is very useful when developing and debugging a report. Here's an example: 

```{r echo=TRUE}
num <- 5
sum <- sum(test_query2(num))
print(sum)
```

## Introduction 
It is generally agreed upon that the prison system in the US is one of the most egregious examples of institutional racism to be found in the country. One of the many social and political factors that contributed to the disproportionate number of people of color who are incarcerated is over-policing. This disparity in incarceration rates can be attributed to a wide range of other factors, so in this report, we are going to find out more about incarceration. How has the prison population changed since 1970s, which state/states is/are have the largest growth of the prison population, also we are going to find out if there is a inequality between genders and races.

## Data Summary 
[TODO]

[TODO ... other sections ... See Canvas for details]

_All the very best with your work!_

